### 2014-04-16 doc/uist14/iteration3.tex
added section name, use studyquote

@@

\subsection{Evaluation}
We evaluate the head motion refinement method by holding an informal study and collecting qualitative feedback from a subset of 4 users from the Iteration 2 study. In the study, we asked users to try cycling through the targets using the new quasi-mode.
The users had strong preferences for the new method of refinement. On a scale from 1-7, 1 being the least mental effort and 7 being the most mental effort users rated the old technique 4.25 and the new technique 2 on average. 100\% indicated a preference for head movement to list navigation. One user referenced the issue of naming targets that the list necessitates, preferring the experience of ``matching visual cues rather than numbers''. Another participant remarked that it ``just made more sense'' and was a ``more natural way for demonstrating intentionality.'' The users prefered the new mapping in relation to the whole environment: ``it leveraged the spatial sense that I already had just by using the system''. They were also delighted to avoid list navigation, which they now called ``difficult'' and ``painful''.

>>>>

%!TEX root = uist14.tex
\section{Iteration 3: Head motion refinement}
\label{sec:iteration-3:-head}

Both {\em Naive IR} and {\em Intensity IR} rely on list navigation on the near-eye display for the refinement step. The list interface has a few clear shortcomings: navigation actions map poorly to real world results, and the users must switch their focus back and forth between the physical scene and the near-eye display. These problems motivated us to design an approach that harnesses the head orientation during the {\em refinement} stage.

In our third iteration, we build a system which further minimizes the chance of falling back to list based {\em refinement}.

@@

\subsection{Evaluation}
We evaluate the head motion refinement method by holding an informal study and collecting qualitative feedback from a subset of 4 users from the Iteration 2 study. In the study, we asked users to try cycling through the targets using the new quasi-mode.

The users had strong preferences for the new method of refinement. On a scale from 1-7, 1 being the least mental effort and 7 being the most mental effort users rated the old technique 4.25 and the new technique 2 on average. 100\% indicated a preference for head movement to list navigation. One user referenced the issue of naming targets that the list necessitates, preferring the experience of \studyquote{matching visual cues rather than numbers}. Another participant remarked that it \studyquote{just made more sense} and was a \studyquote{more natural way for demonstrating intentionality}. The users preferred the new mapping in relation to the whole environment: \studyquote{it leveraged the spatial sense that I already had just by using the system}. They were also delighted to avoid list navigation, which they now called \studyquote{difficult} and \studyquote{painful}.
